Spatiotemporal Multi-Resolution Approximation of the Amari Type Neural Field Model

### 2012-02-04 Multiresolution_framework/ltx/manuscript.tex

The multi-resolution approximation \citep{Mallat1989a} of the neural IDE (MRAIDE) is obtained by decomposing both the field, $v_t(\cdot)$, and the connectivity kernel, $w(\cdot)$, (assuming square-integrable functions) using translations and dilations of a scaling function $\phi(\mathbf{r})$ and a mother wavelet $\psi(\mathbf{r})$. Considering a  one-dimensional field, the static connectivity kernel is decomposed as,
\begin{equation}
 w\left(r\right)=\sum_{l\in \mathbb{Z}}\alpha_{j_0,l} \underbrace{\phi_{j_0,l}\left(r\right)}_{\text{scaling functions}} + \sum_{j\geq j_0}^{\infty} \sum_{l \in \mathbb{Z}}\beta_{j,l} \underbrace{\psi_{j,l}\left(r\right)}_{\text{wavelets}}, 
\label{eq:KernelExpansion}
\end{equation}
where $\alpha_{j_0,l}$ are the approximation coefficients at the lowest scale $j_0$, and $\beta_{j,l}$ are the detail coefficients at different scales $j$, with
\begin{align}
\phi_{j,l}\left(r\right) =& 2^{\frac{j}{2}}\phi\left(2^j r-l\right) \\	
\psi_{j,l}\left(r\right) =& 2^{\frac{j}{2}}\psi\left(2^j r-l\right).
\end{align}
The parameters $j$ and $l$ control the scale (dilation) and translation (spatial shift), respectively. \dean{NEED SOMETHING ABOUT HOW j AND l ARE SET HERE - AS IN THAT THEY ARE KNOWN - AND THAT WE ONLY NEED TO ESTIMATE THE COEFFICIENTS.} \parham{The number of spatial shifts is dependent on the scale, $j$, and can be chosen such that the basis functions cover the spatial domain of interest. The number of scales depends on the spectral characteristics of the field, which will be described later.} Scaling functions retain the lowest frequency components, due to their low-pass properties, while the wavelet functions extract successively higher frequency components due to their band-pass characteristics. 
% At each spatial scale indexed by $j$ (level of decomposition), the neural field can be written as
% \begin{equation}
% 	v_{j,t}\left(\mathbf{r}\right) = \begin{cases}
% 	\sum_{l \in \mathbb{Z}}x_{j,l}(t) \underbrace{\phi_{j,l}\left(\mathbf{r}\right)}_{\text{scaling function}} + \check{x}_{t,j,l}\underbrace{\psi_{j,l}\left(\mathbf{r}\right)}_{\text{mother wavelet}} & \text{if $j=0$},\\
% 	\sum_{l \in \mathbb{Z}}\check{x}_{t,j,l}\psi_{j,l}\left(\mathbf{r}\right) & \text{otherwise}
% \end{cases}
% \end{equation}
The dynamic neural field is decomposed using
\begin{equation}
 v_t\left(r\right)=\sum_{l \in \mathbb{Z}}x_{t,j_{0},l} \underbrace{\phi_{j_0,l}\left(r\right)}_{\text{scaling functions}} + \sum_{j\geq j_0}^{\infty} \sum_{l \in \mathbb{Z}^n} \check{x}_{t,j,l} \underbrace{\psi_{j,l}\left(r\right)}_{\text{wavelets}},
\label{eq:FieldExpansion}
\end{equation}
where $x_{t,j_{0},l}$ and $\check{x}_{t,j,l} $ are the dynamic coefficients of the expansion, constituting the state vector at time $t$. The decomposition enables a separation of the static spatial characteristics, which are considered static functions, that are weighted by dynamic coefficients.

>>>>

The multi-resolution approximation \citep{Mallat1989a} of the neural IDE (MRAIDE) is obtained by decomposing both the field, $v_t(\cdot)$, and the connectivity kernel, $w(\cdot)$, (assuming square-integrable functions) using translations and dilations of a scaling function $\phi(\mathbf{r})$ and a mother wavelet $\psi(\mathbf{r})$. Considering a  one-dimensional field, the static connectivity kernel is decomposed as,
\begin{equation}
 w\left(r\right)=\sum_{l\in \mathbb{Z}}\alpha_{j_0,l} \underbrace{\phi_{j_0,l}\left(r\right)}_{\text{scaling functions}} + \sum_{j\geq j_0}^{\infty} \sum_{l \in \mathbb{Z}}\beta_{j,l} \underbrace{\psi_{j,l}\left(r\right)}_{\text{wavelets}}, 
\label{eq:KernelExpansion}
\end{equation}
where $\alpha_{j_0,l}$ are the approximation coefficients at the lowest scale $j_0$, and $\beta_{j,l}$ are the detail coefficients at different scales $j$, with
\begin{align}
\phi_{j,l}\left(r\right) =& 2^{\frac{j}{2}}\phi\left(2^j r-l\right) \\	
\psi_{j,l}\left(r\right) =& 2^{\frac{j}{2}}\psi\left(2^j r-l\right).
\end{align}
The parameters $j$ and $l$ control the scale (dilation) and translation (spatial shift), respectively. \dean{NEED SOMETHING ABOUT HOW j AND l ARE SET HERE - AS IN THAT THEY ARE KNOWN - AND THAT WE ONLY NEED TO ESTIMATE THE COEFFICIENTS.} \parham{The number of spatial shifts, $l$, is dependent on the scale, $j$, and can be chosen such that the basis functions cover the spatial domain of interest. The number of scales depends on the spectral characteristics of the field, which will be described later.} Scaling functions retain the lowest frequency components, due to their low-pass properties, while the wavelet functions extract successively higher frequency components due to their band-pass characteristics.

% At each spatial scale indexed by $j$ (level of decomposition), the neural field can be written as
% \begin{equation}
% 	v_{j,t}\left(\mathbf{r}\right) = \begin{cases}
% 	\sum_{l \in \mathbb{Z}}x_{j,l}(t) \underbrace{\phi_{j,l}\left(\mathbf{r}\right)}_{\text{scaling function}} + \check{x}_{t,j,l}\underbrace{\psi_{j,l}\left(\mathbf{r}\right)}_{\text{mother wavelet}} & \text{if $j=0$},\\
% 	\sum_{l \in \mathbb{Z}}\check{x}_{t,j,l}\psi_{j,l}\left(\mathbf{r}\right) & \text{otherwise}
% \end{cases}
% \end{equation}
The dynamic neural field is decomposed using
\begin{equation}
 v_t\left(r\right)=\sum_{l \in \mathbb{Z}}x_{t,j_{0},l} \underbrace{\phi_{j_0,l}\left(r\right)}_{\text{scaling functions}} + \sum_{j\geq j_0}^{\infty} \sum_{l \in \mathbb{Z}^n} \check{x}_{t,j,l} \underbrace{\psi_{j,l}\left(r\right)}_{\text{wavelets}},
\label{eq:FieldExpansion}
\end{equation}
where $x_{t,j_{0},l}$ and $\check{x}_{t,j,l} $ are the dynamic coefficients of the expansion, constituting the state vector at time $t$. The decomposition enables a separation of the static spatial characteristics, which are considered static functions, that are weighted by dynamic coefficients.
